Robust background subtraction in traffic environments

### 2019-02-18 paper/Paper.tex
a

\subsection{parameter settings}
The proposed method has a multitude of tunable parameters, their values have been chosen focusing the attention on having an algorithm robust to changing on weather condition and capable of identifying foreground object even if they stay steady for a period of time (i.e. cars stopped to a traffic light). \newline
Experimental results have been shown that the optimal parameters are the following:
\begin{itemize}
\item $N = 30:$ The number of components of the
background model. Increasing the value of this parameter let the algorithm be more robust to noise, but at the same time, increase a lot the time complexity. The value has been choosen considering the previous tradeoff.
\item $K = 3:$ The number of components that have to
be closer than $R(x_i)$ in order to set the pixel to be background.
\item $R_{incdec} = 0.05:$ The rate, at which the decision
threshold $R(x_i)$ is regulated by the controller. 
\item $R_{lower}=18:$ Lower bound of the decision threshold. It has been left to the default value.
\item $R_{scale}=2$ Scaling factor in the controller for the
decision threshold. Lowering it from 5 to 2 has shown to let the algorithm to recognize better the foreground object introducing very low noise.
\item $T_{dec} = 0.05:$ If $x_i$ is background, $T_{dec}$ is the rate at which $T(x_i)$ is decreased.
\item $T_{inc} = 5:$ If $x_i$ is foreground, $T_{inc}$ is the rate at which $T(x_i)$ is increased. These parameter has shown to be very important to keep classified as foreground pixels associated to objects that have stopped their movement. Increasing it to 5 from the proposed value of 2 reduces faster the probability to put a steady foreground object in to one of the N components of the background model.
\item $T_{lower}= 2:$ Lower bound of $T(x_i)$.
\item $T_{upper}= 200:$ Upper bound of $T(x_i)$.
\end{itemize}

>>>>

\subsection{Post-processing}
To enhance the performance of the algorithm is applied on the final mask a median-filter using a square kernel. Since the value of the pixels can be 0 or 255 is equivalent to perform a majority voting among the kernel's pixels to decide the value of the middle one. That has shown to reduce the noise on the final mask and in the meanwhile generate more connected components.

\subsection{parameter settings}
The proposed method has a multitude of tunable parameters, their values have been chosen focusing the attention on having an algorithm robust to changing on weather condition and capable of identifying foreground object even if they stay steady for a period of time (i.e. cars stopped to a traffic light). \newline
Experimental results have been shown that the optimal parameters are the following:
\begin{itemize}
\item $N = 30:$ The number of components of the
background model. Increasing the value of this parameter let the algorithm be more robust to noise, but at the same time, increase a lot the time complexity. The value has been choosen considering the previous tradeoff.
\item $K = 3:$ The number of components that have to
be closer than $R(x_i)$ in order to set the pixel to be background.
\item $R_{incdec} = 0.05:$ The rate, at which the decision
threshold $R(x_i)$ is regulated by the controller. 
\item $R_{lower}=18:$ Lower bound of the decision threshold. It has been left to the default value.
\item $R_{scale}=2$ Scaling factor in the controller for the
decision threshold. Lowering it from 5 to 2 has shown to let the algorithm to recognize better the foreground object introducing very low noise.
\item $T_{dec} = 0.05:$ If $x_i$ is background, $T_{dec}$ is the rate at which $T(x_i)$ is decreased. Decreasing it too fast can lead to include in the background model parts of foreground objects.
\item $T_{inc} = 5:$ If $x_i$ is foreground, $T_{inc}$ is the rate at which $T(x_i)$ is increased. These parameter has shown to be very important to keep classified as foreground pixels associated to objects that have stopped their movement. Increasing it to 5 from the proposed value of 2 reduces faster the probability to put a steady foreground object in to one of the N components of the background model.
\item $T_{lower}= 2:$ Lower bound of $T(x_i)$. It has been set to the value chosen in the original paper.
\item $T_{upper}= 200:$ Upper bound of $T(x_i)$. It has been set to the value chosen in the original paper. 
\end{itemize}
